Exploring Multi-Scale Spatiotemporal Twitter User Mobility Patterns

### 2016-10-19 Multi-scale_Mobility_Pattern_CEUS/template-num.tex
init ref

\title{}

@@

\begin{thebibliography}{00}
\bibitem{zheng2008understanding}
Zheng, Y., Li, Q., Chen, Y., Xie, X., Ma, W.Y., 2008
\newblock Understanding mobility based on GPS data.
\newblock  Proceedings of the 10th international conference on Ubiquitous
  computing. ACM, pp. 312--321.

\bibitem{jiang2009characterizing}
Jiang, B., Yin, J., Zhao, S., 2009
\newblock Characterizing the human mobility pattern in a large street network.
\newblock {\em Physical Review E}, {\em 80},~021136.

\bibitem{belik2011natural}
Belik, V., Geisel, T., Brockmann, D.
\newblock Natural human mobility patterns and spatial spread of infectious
  diseases.
\newblock {\em Physical Review X} {\bf 2011}, {\em 1},~011001.

\bibitem{greenwood1985human}
Greenwood, M.J.
\newblock Human migration: Theory, models, and empirical studies.
\newblock {\em Journal of regional Science} {\bf 1985}, {\em 25},~521--544.

\bibitem{brockmann2006scaling}
Brockmann, D., Hufnagel, L., Geisel, T.
\newblock The scaling laws of human travel.
\newblock {\em Nature} {\bf 2006}, {\em 439},~462--465.

\bibitem{gonzalez2008understanding}
Gonzalez, M.C., Hidalgo, C.A., Barabasi, A.L.
\newblock Understanding individual human mobility patterns.
\newblock {\em Nature} {\bf 2008}, {\em 453},~779--782.

\bibitem{Jurdak2015}
Jurdak, R., Zhao, K., Liu, J., AbouJaoude, M., Cameron, M., Newth, D.
\newblock Understanding Human Mobility from Twitter.
\newblock {\em PLoS ONE} {\bf 2015}, {\em 10},~e0131469.

\bibitem{rhee2011levy}
Rhee, I., Shin, M., Hong, S., Lee, K., Kim, S.J., Chong, S.
\newblock On the levy-walk nature of human mobility.
\newblock {\em IEEE/ACM transactions on networking (TON)} {\bf 2011}, {\em
  19},~630--643.

\bibitem{sevtsuk2010does}
Sevtsuk, A., Ratti, C.
\newblock Does urban mobility have a daily routine? Learning from the aggregate
  data of mobile networks.
\newblock {\em Journal of Urban Technology} {\bf 2010}, {\em 17},~41--60.

\bibitem{kung2014exploring}
Kung, K.S., Greco, K., Sobolevsky, S., Ratti, C.
\newblock Exploring universal patterns in human home-work commuting from mobile
  phone data.
\newblock {\em PloS one} {\bf 2014}, {\em 9},~e96180.

\bibitem{thatcher2014living}
Thatcher, J.
\newblock Living on fumes: Digital footprints, data fumes, and the limitations
  of spatial big data.
\newblock {\em International Journal of Communication} {\bf 2014}, {\em
  8},~1765--1783.

\bibitem{hawelka2014geo}
Hawelka, B., Sitko, I., Beinat, E., Sobolevsky, S., Kazakopoulos, P., Ratti, C.
\newblock Geo-located Twitter as proxy for global mobility patterns.
\newblock {\em Cartography and Geographic Information Science} {\bf 2014}, {\em
  41},~260--271.

\bibitem{giannotti2008mobility}
Giannotti, F., Pedreschi, D.
\newblock {\em Mobility, data mining and privacy: Geographic knowledge
  discovery}, Springer Science \& Business Media,  2008.

\bibitem{crampton2014collect}
Crampton, J.W.
\newblock Collect it all: national security, Big Data and governance.
\newblock {\em GeoJournal} {\bf 2014}, pp. 1--13.

\bibitem{wu2014intra}
Wu, L., Zhi, Y., Sui, Z., Liu, Y.
\newblock Intra-urban human mobility and activity transition: Evidence from
  social media check-in data.
\newblock {\em PloS one} {\bf 2014}, {\em 9},~e97010.

\bibitem{hasan2013understanding}
Hasan, S., Zhan, X., Ukkusuri, S.V.
\newblock Understanding urban human activity and mobility patterns using
  large-scale location-based data from online social media.
\newblock  Proceedings of the 2nd ACM SIGKDD international workshop on urban
  computing. ACM,  2013, p.~6.

\bibitem{cho2011friendship}
Cho, E., Myers, S.A., Leskovec, J.
\newblock Friendship and mobility: user movement in location-based social
  networks.
\newblock  Proceedings of the 17th ACM SIGKDD international conference on
  Knowledge discovery and data mining. ACM,  2011, pp. 1082--1090.

\bibitem{noulas2012tale}
Noulas, A., Scellato, S., Lambiotte, R., Pontil, M., Mascolo, C.
\newblock A tale of many cities: universal patterns in human urban mobility.
\newblock {\em PloS one} {\bf 2012}, {\em 7},~e37027.

\bibitem{balcan2009multiscale}
Balcan, D., Colizza, V., Gon{\c{c}}alves, B., Hu, H., Ramasco, J.J.,
  Vespignani, A.
\newblock Multiscale mobility networks and the spatial spreading of infectious
  diseases.
\newblock {\em Proceedings of the National Academy of Sciences} {\bf 2009},
  {\em 106},~21484--21489.

\bibitem{tamerius2011global}
Tamerius, J., Nelson, M.I., Zhou, S.Z., Viboud, C., Miller, M.A., Alonso, W.J.
\newblock Global influenza seasonality: reconciling patterns across temperate
  and tropical regions.
\newblock {\em Environmental health perspectives} {\bf 2011}, {\em 119},~439.

\bibitem{tsou2015}
Tsou, M.H.
\newblock Research challenges and opportunities in mapping social media and Big
  Data.
\newblock {\em Cartography and Geographic Information Science} {\bf 2015}, {\em
  42},~70--74.

\bibitem{zheng2010geolife}
Zheng, Y., Xie, X., Ma, W.Y.
\newblock GeoLife: A Collaborative Social Networking Service among User,
  Location and Trajectory. {\bf 2010}.

\bibitem{becker2013human}
Becker, R., C{\'a}ceres, R., Hanson, K., Isaacman, S., Loh, J.M., Martonosi,
  M., Rowland, J., Urbanek, S., Varshavsky, A., Volinsky, C.
\newblock Human mobility characterization from cellular network data.
\newblock {\em Communications of the ACM} {\bf 2013}, {\em 56},~74--82.

\bibitem{sobolevsky2013delineating}
Sobolevsky, S., Szell, M., Campari, R., Couronn{\'e}, T., Smoreda, Z., Ratti,
  C.
\newblock Delineating geographical regions with networks of human interactions
  in an extensive set of countries.
\newblock {\em PLoS One} {\bf 2013}, {\em 8},~e81707.

\bibitem{twitterAPI}
Twitter.
\newblock Twitter streaming API.
\newblock {\em available from: https://dev.twitter.com/streaming/overview} {\bf
  2016}.

\bibitem{cranshaw2012livehoods}
Cranshaw, J., Schwartz, R., Hong, J.I., Sadeh, N.M.
\newblock The Livehoods Project: Utilizing Social Media to Understand the
  Dynamics of a City.
\newblock  ICWSM,  2012.

\bibitem{mitchell2013geography}
Mitchell, L., Frank, M.R., Harris, K.D., Dodds, P.S., Danforth, C.M.
\newblock The geography of happiness: Connecting twitter sentiment and
  expression, demographics, and objective characteristics of place {\bf 2013}.

\bibitem{longley2015geotemporal}
Longley, P.A., Adnan, M., Lansley, G., others.
\newblock The geotemporal demographics of Twitter usage.
\newblock {\em Environment and Planning A} {\bf 2015}, {\em 47},~465--484.

\bibitem{hagerstrand1985time}
H{\"a}gerstrand, T., others.
\newblock Time-geography: focus on the corporeality of man, society, and
  environment.
\newblock {\em The science and praxis of complexity} {\bf 1985}, pp. 193--216.

\bibitem{kwan2004geovisualization}
Kwan, M.P., Lee, J.
\newblock Geovisualization of human activity patterns using 3D GIS: a
  time-geographic approach.
\newblock {\em Spatially integrated social science} {\bf 2004}, {\em 27}.

\bibitem{andrienko2007designing}
Andrienko, N., Andrienko, G.
\newblock Designing visual analytics methods for massive collections of
  movement data.
\newblock {\em Cartographica: The International Journal for Geographic
  Information and Geovisualization} {\bf 2007}, {\em 42},~117--138.

\bibitem{maceachren2001research}
MacEachren, A.M., Kraak, M.J.
\newblock Research challenges in geovisualization.
\newblock {\em Cartography and Geographic Information Science} {\bf 2001}, {\em
  28},~3--12.

\bibitem{maceachren2004maps}
MacEachren, A.M.
\newblock {\em How maps work: representation, visualization, and design},
  Guilford Press,  2004.

\bibitem{andrienko2007visual}
Andrienko, G., Andrienko, N., Wrobel, S.
\newblock Visual analytics tools for analysis of movement data.
\newblock {\em ACM SIGKDD Explorations Newsletter} {\bf 2007}, {\em 9},~38--46.

\bibitem{black2012twitter}
Black, A., Mascaro, C., Gallagher, M., Goggins, S.P.
\newblock Twitter zombie: Architecture for capturing, socially transforming and
  analyzing the Twittersphere.
\newblock  Proceedings of the 17th ACM international conference on Supporting
  group work. ACM,  2012, pp. 229--238.

\bibitem{shvachko2010hadoop}
Shvachko, K., Kuang, H., Radia, S., Chansler, R.
\newblock The hadoop distributed file system.
\newblock  Mass Storage Systems and Technologies (MSST), 2010 IEEE 26th
  Symposium on. IEEE,  2010, pp. 1--10.

\bibitem{dean2008mapreduce}
Dean, J., Ghemawat, S.
\newblock MapReduce: simplified data processing on large clusters.
\newblock {\em Communications of the ACM} {\bf 2008}, {\em 51},~107--113.

\bibitem{gao2012exploring}
Gao, H., Tang, J., Liu, H.
\newblock Exploring Social-Historical Ties on Location-Based Social Networks.
\newblock  ICWSM,  2012.

\bibitem{buttenfield1991map}
Buttenfield, B.P., McMaster, R.B.
\newblock {\em Map Generalization: Making rules for knowledge representation},
  Longman Scientific \& Technical New York,  1991.

\bibitem{samet1984quadtree}
Samet, H.
\newblock The quadtree and related hierarchical data structures.
\newblock {\em ACM Computing Surveys (CSUR)} {\bf 1984}, {\em 16},~187--260.

\bibitem{clauset2009power}
Clauset, A., Shalizi, C.R., Newman, M.E.
\newblock Power-law distributions in empirical data.
\newblock {\em SIAM review} {\bf 2009}, {\em 51},~661--703.

\bibitem{reynolds2012truncated}
Reynolds, A.
\newblock Truncated L{\'e}vy walks are expected beyond the scale of data
  collection when correlated random walks embody observed movement patterns.
\newblock {\em Journal of The Royal Society Interface} {\bf 2012}, {\em
  9},~528--534.

\bibitem{zhao2015explaining}
Zhao, K., Musolesi, M., Hui, P., Rao, W., Tarkoma, S.
\newblock Explaining the power-law distribution of human mobility through
  transportation modality decomposition.
\newblock {\em Scientific reports} {\bf 2015}, {\em 5}.

>>>>

\title{Exploring Multi-Scale Spatiotemporal Twitter User Mobility Patterns}

@@

\begin{thebibliography}{00}
\bibitem{zheng2008understanding}
Zheng, Y., Li, Q., Chen, Y., Xie, X., Ma, W.Y., 2008. Understanding mobility based on GPS data. Proceedings of the 10th international conference on Ubiquitous computing. ACM, pp. 312--321.

\bibitem{jiang2009characterizing}
Jiang, B., Yin, J., Zhao, S., 2009. Characterizing the human mobility pattern in a large street network. {\em Physical Review E}, {\em 80},~021136.

\bibitem{belik2011natural}
Belik, V., Geisel, T., Brockmann, D., 2011. Natural human mobility patterns and spatial spread of infectious diseases. {\em Physical Review X}, {\em 1},~011001.

\bibitem{greenwood1985human}
Greenwood, M.J., 1985. Human migration: Theory, models, and empirical studies. {\em Journal of regional Science}, {\em 25}, pp. 521--544.

\bibitem{brockmann2006scaling}
Brockmann, D., Hufnagel, L., Geisel, T., 2006. The scaling laws of human travel. {\em Nature}, {\em 439}, pp. 462--465.

\bibitem{gonzalez2008understanding}
Gonzalez, M.C., Hidalgo, C.A., Barabasi, A.L., 2008. Understanding individual human mobility patterns. {\em Nature}, {\em 453}, pp. 779--782.

\bibitem{Jurdak2015}
Jurdak, R., Zhao, K., Liu, J., AbouJaoude, M., Cameron, M., Newth, D., 2015. Understanding Human Mobility from Twitter. {\em PLoS ONE}, {\em 10},~e0131469.

\bibitem{rhee2011levy}
Rhee, I., Shin, M., Hong, S., Lee, K., Kim, S.J., Chong, S., 2011. On the levy-walk nature of human mobility. {\em IEEE/ACM transactions on networking (TON)}, {\em 19}, pp. 630--643.

\bibitem{sevtsuk2010does}
Sevtsuk, A., Ratti, C., 2010. Does urban mobility have a daily routine? Learning from the aggregate data of mobile networks. {\em Journal of Urban Technology}, {\em 17}, pp. 41--60.

\bibitem{kung2014exploring}
Kung, K.S., Greco, K., Sobolevsky, S., Ratti, C. 2014. Exploring universal patterns in human home-work commuting from mobile phone data. {\em PLoS ONE}, {\em 9},~e96180.

\bibitem{thatcher2014living}
Thatcher, J., 2014. Living on fumes: Digital footprints, data fumes, and the limitations of spatial big data. {\em International Journal of Communication}, {\em 8}, pp. 1765--1783.

\bibitem{hawelka2014geo}
Hawelka, B., Sitko, I., Beinat, E., Sobolevsky, S., Kazakopoulos, P., Ratti, C., 2014. Geo-located Twitter as proxy for global mobility patterns.{\em Cartography and Geographic Information Science}, {\em
  41}, pp. 260--271.

\bibitem{giannotti2008mobility}
Giannotti, F., Pedreschi, D., 2008.{\em Mobility, data mining and privacy: Geographic knowledge discovery}, Springer Science \& Business Media.

\bibitem{crampton2014collect}
Crampton, J.W. 2014. Collect it all: national security, Big Data and governance. {\em GeoJournal}, pp. 1--13.

\bibitem{wu2014intra}
Wu, L., Zhi, Y., Sui, Z., Liu, Y., 2014. Intra-urban human mobility and activity transition: Evidence from social media check-in data. {\em PLoS ONE}, {\em 9},~e97010.

\bibitem{hasan2013understanding}
Hasan, S., Zhan, X., Ukkusuri, S.V., 2013. Understanding urban human activity and mobility patterns using large-scale location-based data from online social media. Proceedings of the 2nd ACM SIGKDD international workshop on urban computing. ACM,  2013, p.~6.

\bibitem{cho2011friendship}
Cho, E., Myers, S.A., Leskovec, J. 2011, Friendship and mobility: user movement in location-based social networks. Proceedings of the 17th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM,  2011, pp. 1082--1090.

\bibitem{noulas2012tale}
Noulas, A., Scellato, S., Lambiotte, R., Pontil, M., Mascolo, C., 2012. A tale of many cities: universal patterns in human urban mobility. {\em PLoS ONE}, {\em 7},~e37027.

\bibitem{balcan2009multiscale}
Balcan, D., Colizza, V., Gon{\c{c}}alves, B., Hu, H., Ramasco, J.J.,
  Vespignani, A., 2009. Multiscale mobility networks and the spatial spreading of infectious diseases.{\em Proceedings of the National Academy of Sciences},{\em 106}, pp. 21484--21489.

\bibitem{tamerius2011global}
Tamerius, J., Nelson, M.I., Zhou, S.Z., Viboud, C., Miller, M.A., Alonso, W.J., 2011. Global influenza seasonality: reconciling patterns across temperate and tropical regions.{\em Environmental health perspectives}, {\em 119},~439.

\bibitem{tsou2015}
Tsou, M.H., 2015. Research challenges and opportunities in mapping social media and Big Data.{\em Cartography and Geographic Information Science} {\bf 2015}, {\em 42}, pp. 70--74.

\bibitem{zheng2010geolife}
Zheng, Y., Xie, X., Ma, W.Y., 2010. GeoLife: A Collaborative Social Networking Service among User, Location and Trajectory.

\bibitem{becker2013human}
Becker, R., C{\'a}ceres, R., Hanson, K., Isaacman, S., Loh, J.M., Martonosi,
  M., Rowland, J., Urbanek, S., Varshavsky, A., Volinsky, C., 2013. Human mobility characterization from cellular network data.{\em Communications of the ACM}, {\em 56}, pp. 74--82.

\bibitem{sobolevsky2013delineating}
Sobolevsky, S., Szell, M., Campari, R., Couronn{\'e}, T., Smoreda, Z., Ratti,
  C., 2013. Delineating geographical regions with networks of human interactions in an extensive set of countries.{\em PLoS ONE}, {\em 8},~e81707.

\bibitem{twitterAPI}
Twitter, 2016. Twitter streaming API.{\em Available from: https://dev.twitter.com/streaming/overview}.

\bibitem{cranshaw2012livehoods}
Cranshaw, J., Schwartz, R., Hong, J.I., Sadeh, N.M., 2012. The Livehoods Project: Utilizing Social Media to Understand the Dynamics of a City. ICWSM.

\bibitem{mitchell2013geography}
Mitchell, L., Frank, M.R., Harris, K.D., Dodds, P.S., Danforth, C.M., 2013. The geography of happiness: Connecting twitter sentiment and expression, demographics, and objective characteristics of place.

\bibitem{longley2015geotemporal}
Longley, P.A., Adnan, M., Lansley, G., others., 2015. The geotemporal demographics of Twitter usage. {\em Environment and Planning A}, {\em 47}, pp. 465--484.

\bibitem{hagerstrand1985time}
H{\"a}gerstrand, T., others., 1985. Time-geography: focus on the corporeality of man, society, and environment. {\em The science and praxis of complexity}, pp. 193--216.

\bibitem{kwan2004geovisualization}
Kwan, M.P., Lee, J., 2004. Geovisualization of human activity patterns using 3D GIS: a time-geographic approach. {\em Spatially integrated social science}, {\em 27}.

\bibitem{andrienko2007designing}
Andrienko, N., Andrienko, G., 2007. Designing visual analytics methods for massive collections of movement data. {\em Cartographica: The International Journal for Geographic Information and Geovisualization}, {\em 42}, pp. 117--138.

\bibitem{maceachren2001research}
MacEachren, A.M., Kraak, M.J., 2001. Research challenges in geovisualization. {\em Cartography and Geographic Information Science}, {\em
  28}, pp. 3--12.

\bibitem{maceachren2004maps}
MacEachren, A.M., 2004. {\em How maps work: representation, visualization, and design}, Guilford Press.

\bibitem{andrienko2007visual}
Andrienko, G., Andrienko, N., Wrobel, S., 2007. Visual analytics tools for analysis of movement data. {\em ACM SIGKDD Explorations Newsletter}, {\em 9}, pp. 38--46.

\bibitem{black2012twitter}
Black, A., Mascaro, C., Gallagher, M., Goggins, S.P., 2012. Twitter zombie: Architecture for capturing, socially transforming and analyzing the Twittersphere. Proceedings of the 17th ACM international conference on Supporting group work. ACM, pp. 229--238.

\bibitem{shvachko2010hadoop}
Shvachko, K., Kuang, H., Radia, S., Chansler, R., 2010. The hadoop distributed file system. Mass Storage Systems and Technologies (MSST), 2010 IEEE 26th Symposium on. IEEE, 2010, pp. 1--10.

\bibitem{dean2008mapreduce}
Dean, J., Ghemawat, S., 2008. MapReduce: simplified data processing on large clusters. {\em Communications of the ACM}, {\em 51}, pp. 107--113.

\bibitem{gao2012exploring}
Gao, H., Tang, J., Liu, H., 2012. Exploring Social-Historical Ties on Location-Based Social Networks. ICWSM.

\bibitem{buttenfield1991map}
Buttenfield, B.P., McMaster, R.B., 1991. {\em Map Generalization: Making rules for knowledge representation}, Longman Scientific \& Technical New York.

\bibitem{samet1984quadtree}
Samet, H., 1984. The quadtree and related hierarchical data structures. {\em ACM Computing Surveys (CSUR)}, {\em 16}, pp. 187--260.

\bibitem{clauset2009power}
Clauset, A., Shalizi, C.R., Newman, M.E., 2009. Power-law distributions in empirical data. {\em SIAM review}, {\em 51}, pp. 661--703.

\bibitem{reynolds2012truncated}
Reynolds, A., 2012. Truncated L{\'e}vy walks are expected beyond the scale of data collection when correlated random walks embody observed movement patterns. {\em Journal of The Royal Society Interface}, {\em
  9}, pp. 528--534.

\bibitem{zhao2015explaining}
Zhao, K., Musolesi, M., Hui, P., Rao, W., Tarkoma, S., 2015. Explaining the power-law distribution of human mobility through transportation modality decomposition. {\em Scientific reports}, {\em 5}.
